Why there are more species in several small patches vs few large patches:

### 2024-03-11 ms_SLOSS.Rmd
Changes to discussion and figure caption

![Examples of species spatial pattern before and after fragmentation for the neutral model.  Simulations were performed using a fixed growth rate ($\lambda=2$), migration rate of 0.0001 and dispersal distance 1.5. A. & B. spatial pattern before fragmentation. C. & D. Spatial pattern after fragmentation where 60% of the habitat was destroyed (Purple color), with patch-sizes 3 (C) and 29 (D).  E. & F. Spatial pattern after 600 time steps where the extinction of populations is observed at smaller patch-size (E)](Figures/ModelSpatialPatternComparison.png)

@@

In neutral models one species by chance tends to dominate a patch [@Hubbell2001], so in fragmented landscapes, once the species increments its density it is unlikely that another species replaces it so with more patches the probability of having more species is augmented. This effect is enhanced when individuals can select the habitat, because of the increased survival of the propagules, thus fragmentation has a positive effect on the number of species. 
For competitive communities, there is a higher probability that different species dominate different smaller patches, compared with a bigger patch. Thus, again fragmentation has a positive effect on the number of species, this effect is called stochastic divergence [@Riva2023]. In smaller patches there is an increase in extinction risk because they support smaller populations [@Laurance2002;@Shafer1995], however as patches become smaller they also become more numerous, reducing the probability of extinction over the entire set of patches due to spreading the risk effect [@Crowley1977]. The combination of these two effects, the stochastic divergence and the risk effect, explain the highest number of species with patch size over the threshold of species survival.

>>>>

![Examples of species spatial patterns before and after fragmentation for the neutral model are illustrated. Different shades from dark green to white represent distinct species, with the destroyed habitat depicted in purple. Simulations were conducted with a fixed growth rate ($\lambda=2$), a migration rate of 0.0001, and a dispersal distance of 1.5. A. & B. showcase spatial patterns before fragmentation. C. & D. depict spatial patterns after fragmentation, where 60% of the habitat was destroyed, with patch sizes of 3 (C) and 29 (D). In these cases, the significance of the species' spatial distribution before fragmentation becomes evident. E. & F. display spatial patterns after 600 time steps, illustrating the extinction of populations at smaller patch sizes (E).](Figures/ModelSpatialPatternComparison.png)

@@

In neutral models, where species are considered equivalent, one species, by chance, tends to dominate a patch (Hubbell, 2001). Consequently, in fragmented landscapes, once a species increases its density, the likelihood of another species replacing it is low. With more patches, the probability of having a greater number of species is heightened. This effect is further amplified when individuals can actively select their habitat, leading to increased survival of propagules. Consequently, fragmentation exhibits a positive influence on the number of species in such scenarios.

For competitive communities, there is a higher probability that different species dominate different smaller patches, compared with a bigger patch. Thus, again fragmentation has a positive effect on the number of species, this effect is called stochastic divergence [@Riva2023]. In smaller patches there is an increase in extinction risk because they support smaller populations [@Laurance2002;@Shafer1995], however as patches become smaller they also become more numerous, reducing the probability of extinction over the entire set of patches due to spreading the risk effect [@Crowley1977]. The combination of these two effects, the stochastic divergence and the risk effect, explain the highest number of species with patch size over the threshold of species survival.
